Comparing Hydrogen and Jet-A for an N+3 Turbofan with Water Recirculation using Gradient-Based Optimization

### 2023-05-09 conference-paper/main.tex
finished presentation and updated paper

@@

@@

\section{Acknowledgements}
We would like to thank Justin Grey for his help with the pyCycle components of this work.
Justin's expertise and knowledge of pyCycle tool helped make the development of the custom pyCycle components possible.

>>>>

\noindent

@@

Additionally, the FAR of the engines with water recovery increases due to a decrease in overall and core mass flow.
An increase in FAR likely requires a larger OPR to maintain the required thrust while minimizing fuel burn.

@@

\section{Acknowledgements}
We would like to thank Justin Grey for his help with the pyCycle components in this work.
Justin's expertise and knowledge of pyCycle tool helped make the development of the custom pyCycle components possible.
